Stepwise Multiple Regressions

### 2021-02-03 Stepwise Multiple Regressions.Rmd
Stepwise Regressions + knit

# Data tidying

```{r}

@@

```{r}

#Select the columns that we want to feed into the model for simplicity
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         max.size.ingest.mm, 
         exposure.duration.d, 
         bio_f, 
         charge, 
         zetapotential.mV, 
         particle.source,
         lvl1_f,
         lvl2_f,
         lvl3,
         effect)

@@

@@

>>>>

# Data Tidying

```{r, echo = FALSE,}

@@

#Model

Doses (count, mass and volume), size (continuous), and exposure duration are all log transformed given histogram results.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
5. Size (binned)
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
10. Charge (negative/positive)
11. Particle Source
12. Organism Group - substitute for body right now

```{r, echo = FALSE}

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         charge, 
         particle.source,
         org_f,
         effect)

```{r, echo = FALSE}

@@

summary(Full_Model)

@@

#Model Refining

##Remove Charge

Complete charge data are limited to PS and PC spheres - remove to include for complete data.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
5. Size (binned)
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
~~10. Charge (negative/positive)~~
11. Particle Source
12. Organism Group - substitute for body right now

```{r, echo = FALSE}

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

```{r, echo = FALSE}

summary(Full_Model)

##Remove Charge + Size (binned)

Size (binned) had the highest p value in the last model - remove.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
~~5. Size (binned)~~
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
~~10. Charge (negative/positive)~~
11. Particle Source
12. Organism Group - substitute for body right now

```{r, echo = FALSE}

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         # size_f, 
         size.length.um.used.for.conversions, 
         shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

```{r, echo = FALSE}

summary(Full_Model)

##Remove Charge + Size (binned) + Shape

Shape had the highest p value in the last model - remove.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
~~5. Size (binned)~~
~~6. Shape~~
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
~~10. Charge (negative/positive)~~
11. Particle Source
12. Organism Group - substitute for body right now

```{r, echo = FALSE}

#Select the columns that we want to feed into the model for simplicity.
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(dose.particles.mL.master, 
         dose.mg.L.master, 
         # size_f, 
         size.length.um.used.for.conversions, 
         # shape_f, 
         poly_f, 
         dose.um3.mL.master, 
         exposure.duration.d, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

```{r, echo = FALSE}

summary(Full_Model)

#Variable Histograms for Numerical Data

Plot histograms of all numerical continuous values to determine if any need log transformation due to severe skew.

```{r, echo = FALSE}

##################################### Log transform needed #########################################################################

#### Dose - Particles/mL ####
Dose_Particles_mL <- aoc_setup$dose.particles.mL.master

hist(Dose_Particles_mL)

#Dose - Particles/mL - log transformed
Dose_Particles_mL_log10 <- log10(aoc_setup$dose.particles.mL.master)

hist(Dose_Particles_mL_log10)

#### Dose - mg/L ####
Dose_mg_L <- aoc_setup$dose.mg.L.master

hist(Dose_mg_L)

#Dose - mg/L - log transformed
Dose_mg_L_log10 <- log10(aoc_setup$dose.mg.L.master)

hist(Dose_mg_L_log10)

#### Dose - um3/mL ####
Dose_um3_mL <- aoc_setup$dose.um3.mL.master

hist(Dose_um3_mL)

#Dose - um3/mL - log transformed
Dose_um3_mL_log10 <- log10(aoc_setup$dose.um3.mL.master)

hist(Dose_um3_mL_log10)

#### Size - Continuous ####
Size_Continuous <- aoc_setup$size.length.um.used.for.conversions

hist(Size_Continuous)

#Size - Continuous - log transformed
Size_Continuous_log10 <- log10(aoc_setup$size.length.um.used.for.conversions)

hist(Size_Continuous_log10)

#### Exposure Duration ####
Exposure_Duration <- aoc_setup$exposure.duration.d

hist(Exposure_Duration)

#Exposure Duration - log transformed
Exposure_Duration_log10 <- log10(aoc_setup$exposure.duration.d)

hist(Exposure_Duration_log10)

######################################## Log Transform not needed #################################################################

#### Ingestible Size ####
Max_Ingest <- aoc_setup$max.size.ingest.mm

hist(Max_Ingest)

#### Zeta Potential ####
Zeta <- aoc_setup$zetapotential.mV

hist(Zeta)

#Model - Log Transformed

Doses (count, mass and volume), size (continuous), and exposure duration are all log transformed given histogram results.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
5. Size (binned)
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
10. Charge (negative/positive)
11. Particle Source
12. Organism Group - substitute for body right now

```{r, echo = FALSE}

#Log transform numeric values 
aoc_setup <- aoc_setup %>% 
  mutate(log10(dose.particles.mL.master)) %>% 
  mutate(log10(dose.mg.L.master)) %>%
  mutate(log10(dose.um3.mL.master)) %>%
  mutate(log10(size.length.um.used.for.conversions)) %>%
  mutate(log10(exposure.duration.d))

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         charge, 
         particle.source,
         org_f,
         effect)

```{r, echo = FALSE}

summary(Full_Model)

#Model Refining

##Remove Charge

Complete charge data are limited to PS and PC spheres - remove to include for complete data.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
5. Size (binned)
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
~~10. Charge (negative/positive)~~
11. Particle Source
12. Organism Group - substitute for body right now

```{r, echo = FALSE}

#Log transform numeric values 
aoc_setup <- aoc_setup %>% 
  mutate(log10(dose.particles.mL.master)) %>% 
  mutate(log10(dose.mg.L.master)) %>%
  mutate(log10(dose.um3.mL.master)) %>%
  mutate(log10(size.length.um.used.for.conversions)) %>%
  mutate(log10(exposure.duration.d))

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

```{r, echo = FALSE}

summary(Full_Model)

##Remove Charge + Size (binned)

Size (binned) had the highest p value in the last model - removed.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
~~5. Size (binned)~~
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
~~10. Charge (negative/positive)~~
11. Particle Source
12. Organism Group - substitute for body right now

```{r, echo = FALSE}

#Log transform numeric values 
aoc_setup <- aoc_setup %>% 
  mutate(log10(dose.particles.mL.master)) %>% 
  mutate(log10(dose.mg.L.master)) %>%
  mutate(log10(dose.um3.mL.master)) %>%
  mutate(log10(size.length.um.used.for.conversions)) %>%
  mutate(log10(exposure.duration.d))

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         # size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         # charge, 
         particle.source,
         org_f,
         effect)

```{r, echo = FALSE}

summary(Full_Model)

##Remove Charge + Size (binned) + Particle Source

Particle source had the highest p value in the last model - removed.

The model starts with the following independent variables: 
1. Dose (count)
2. Dose (mass)
3. Dose (volume)
4. Size (continuous)
~~5. Size (binned)~~
6. Shape
7. Polymer
8. Exposure Duration
9. Level of Biological Organization
~~10. Charge (negative/positive)~~
~~11. Particle Source~~
12. Organism Group - substitute for body right now

```{r, echo = FALSE}

#Log transform numeric values 
aoc_setup <- aoc_setup %>% 
  mutate(log10(dose.particles.mL.master)) %>% 
  mutate(log10(dose.mg.L.master)) %>%
  mutate(log10(dose.um3.mL.master)) %>%
  mutate(log10(size.length.um.used.for.conversions)) %>%
  mutate(log10(exposure.duration.d))

#Select the columns that we want to feed into the model for simplicity and log transform data according to histogram results. 
aoc_setup_selected <- aoc_setup %>% 
  dplyr::select(`log10(dose.particles.mL.master)`, 
         `log10(dose.mg.L.master)`, 
         # size_f, 
         `log10(size.length.um.used.for.conversions)`, 
         shape_f, 
         poly_f, 
         `log10(dose.um3.mL.master)`, 
        `log10(exposure.duration.d)`, 
         bio_f, 
         # charge, 
         # particle.source,
         org_f,
         effect)

```{r, echo = FALSE}

summary(Full_Model)
